---
title: "Introduction to surveygraph"
description: >
  Getting started with surveygraph.
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Get started}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

```{r, echo = FALSE, message = FALSE, warning = FALSE}
knitr::opts_chunk$set(collapse = T, comment = "#>")
options(tibble.print_min = 4L, tibble.print_max = 4L)
```

This is an introduction to the surveygraph package, a lightweight package that
produces network representations of sociological data. We assume that this data
is presented in a rectangular array like a survey.

We'll start by loading surveygraph:

```{r, message = FALSE}
library(surveygraph)
```

# Similarity measure
## Another heading
## Yet another heading
### Agent layer projection
### Symbolic layer projection

The most important grouping verb is `group_by()`: it takes a data frame and one or more variables to group by:

```{r}
df <- data.frame(item1 = c(1, 2, 3), item2 = c(4, 5, 7))
df
```
